\documentclass{article}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{ {images/} }

\usepackage{geometry}
\geometry{a4paper, left=25mm, right=25mm, top=25mm, bottom=25mm}
\setlength{\parindent}{2em}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.3}


\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sheriden Goldie - 42611814}
\lhead{FOAR705 - Digital Humanities}
\lfoot{Session 2 2019, Macquarie University}
\rfoot{Page \thepage}

\title{Proof of Concept - Scoping Exercise Part 2}
\author{By Sheriden Goldie}
\date{}

\begin{document}

\maketitle

\tableofcontents

\pagebreak

\section{Identification}
In the process of completing a Business Analysis (Scoping Exercise 1) on my research process, I identified some key pain areas for further investigation.

These were:
\begin{itemize}
    \item Note taking and note management.
    \item Formatting, and ability to change format for purpose (without damaging content).
    \item Reference and citation management.
\end{itemize}

\subsection{Problem Identification}
The largest and most time consuming of these pains is ``Note taking and note management.''

The key aspects of this problem are:
\begin{itemize}
    \item Recording notes in a meaningful and organisable way
    \item Documentation of notes - recording note metadata (that being the source material, page numbers, date recorded etc)
    \item Recording and organising personal notes/responses to other notes
    \item Creating networks of meaning from notes - mapping the key terms that link notes (or identifying notes that don't link to others)
    \item Being able to access these notes and their metadata easily during final composition to enable to process of writing to be more flowing.
\end{itemize}

In the articulation above, there are certain points that need to be addressed in order to better express this problem. 
\begin{itemize}
    \item What do I mean by a ``note''? Above I use the word ``note'' to mean two different things - 1. text taken directly from a Source Text, and 2. Text composed myself for the purpose of collating ideas and thoughts
    \item What are the different layers of data/processes that need to be addressed? - There are distinct sections to this process, that can be further separated for the purpose of finding technological solutions.
\end{itemize}

\pagebreak

\section{Clarification}
\subsection{Key Project Terms}

To clarify this problem I am developing a controlled vocabulary of the following terms:
\begin{itemize}
    \item Source text - the written document that information is taken from directly
    \item Quote - a direct transcription from a source text - a key data point.
    \item Source Text Metadata - the information necessary to identify the source text - enabling another person to find that text. Organised in such a way as to be useful for creating in-text citations and reference lists.
    \item Note - text written by the researcher reflecting on the content of a quote - A key data point.
    \item Summary Note - an extended note that might refer to two or more Source Texts and other Notes. 
    \item Tag - a unique category of metadata that is attached to a Quote or Note that enables it to be linked to other quotes or notes. These are established using a controlled vocabulary.
    \item Mapping - the process of finding connections and links between notes and quotes
\end{itemize}

\subsection{Articulation}
The problem I am addressing is the collection, organisation, and synthesis of data within my field of Literary Studies. 

I aim to find a solution that will address the act of recording note and quotes. I aim to find a solution to the organisation of notes and quotes, and metadata that is drawn from Source Texts.  I aim to employ an appropriate way to make this data searchable and transparent. I am also aiming to enable specific data points to be represented visually. 
\pagebreak

\section{Computational Thinking Response}

Considering this problem in terms of computational thinking, I will attempt to apply a practice of Decomposition, Pattern Recognition, and Algorithm Design to the problem of note taking and note organisation I have outlined. Though at this stage the practice of Algorithm design will not be a fully realised articulation, as the full scope of elaboration of available technology has not been completed yet.

\subsection{Decomposition}
Breaking down data, processes, or problems into smaller, manageable parts
The overall process of note taking and note management can be broken into three key parts:
\begin{itemize}
    \item Data Collection - recording quotes and notes
    \item Data Organisation - applying organisational rules to data. Creating a system to find relevant information after it has been recorded
    \item Data Synthesis - Mapping all data points to find connections, themes, and trends
\end{itemize}

The process of data collection can be broken down into the following steps:
\begin{enumerate}
    \item Read Source Text
    \item Write/record a passage or idea from the Source Text. This is being referred to now as a Quote.
    \item Write/record my thoughts and ideas in relation to the Quote - especially in relation to the current research project.
    \item Repeat these steps for numerous Source Texts.
    \item Writing/recording extended Notes which might synthesise ideas into my own words - or that draw some links between two or more Source Texts.
\end{enumerate}

The process of Data Organisation can be broken down into the following steps:
\begin{enumerate}
    \item Use Tags (categories) to add metadata to notes and quotes.
    \item Link Source Text Metadata to notes and quotes.
    \item Use a system that allows data to be searchable and transparent.
\end{enumerate}

The process of Data Synthesis can be broken down into the following steps:
\begin{enumerate}
    \item Collate all Quotes and Notes for review.
    \item Find connections between Quotes and Notes.
    \item Use connected groupings to record more Summary Notes (Refer back to data collection steps).
    \item Use the Networked data to create an essay/project outline.
    \item Have the Quotes, Notes, Summary Notes, and Source Text Metadata available and easily accessible during writing to allow it to be integrated without interrupting the writing flow. 
    \item Use Source Text Metadata to create relevant in-text citations, as well as end of text reference list/bibliography (in the relevant format).
\end{enumerate}

\subsection{Pattern Recognition}
Observing patterns, trends, and regularities in data

In the process I outlined above - there are some processes that seem to be recurring. 

\begin{itemize}
    \item Writing/Recording - including relevant metadata. There are aspects of this that are repetitive like noting the metadata, but the recording of Notes is a cognitive and creative process - which resists digitisation. 
    \item Creating a network of key ideas/key terms (tags) between Notes and Quotes. This is a labour intensive task - and can very easily go haywire, especially if one is using a manual process like post-it notes or various notebook pages. 
    \item Organising data in a way that is accessible and navigateable. This is a task that could definitely be digitised - though it may require adjustments to general work practices. These adjustments could be beneficial in the long run, though challenging to implement.
\end{itemize}

\subsection{Algorithm Design}
Developing the step by step instructions for solving this and similar problems.

A key issue of this problem that I can apply algorithm design to is organising the data in a way that is accessible and navigateable.

Conception of Algorithm Design for Data Collection:
\begin{itemize}
    \item Entering data into a digital format.
    \item Data is entered with sufficient metadata, like tags, in a frame of reference that can be abstracted from the core data.
    \item Creating an output framework for the secondary networked data to be displayed with.
\end{itemize}

Conception of Algorithm Design for Data Organisation:
\begin{enumerate}
    \item Use a digital format to aid the entering of data. 
    \item Enter data in a way that is linked to Tags, and Source Text Metadata
    \item Organise the data using Tags, and Source Text Metadata. This would ideally make this data searchable as well.
\end{enumerate}

Conception of Algorithm Design for Data Synthesis:
\begin{enumerate}
    \item Data is organised using tags.
    \item Use tags as specific data points.
    \item These data points are able to be exported to a program that can visualise these links.
    \item The information in the visualisation is able to link back to the main data/core information.
    \item This visualisation is able to be used to create various output formats that enable mind-mapping style thinking, as well as outlining for document composition.
\end{enumerate}

\end{document}